\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/nipunarora8/}{\Large Nipun Arora}} & Email : \href{mailto:nipunarora8@yahoo.com}{nipunarora8@yahoo.com}\\
  \textbf{M.Sc. Artificial Intelligence | AI Software Engineer} & Mobile : (+49) 17687826567\\
  \href{https://nipunarora8.github.io}   {{nipunarora8.github.io}} || \href{https://www.linkedin.com/in/nipunarora8/}   {{linkedin.com/in/nipunarora8}} & Erlangen, Germany \\
\end{tabular*}

%-----------PROFILE SUMMARY-----------------
\section{Professional Profile}
\resumeSubHeadingListStart
\small

AI graduate and a \textbf{Max Planck Institute} professional with a focus on \textbf{Artificial Intelligence} and \textbf{Computer Vision}. Experienced in solving end-to-end problems by bridging gaps between AI, perception, and hardware. Proven track record of deploying deep learning models on edge devices, currently advancing intelligent autonomy through custom UxV robotics projects.

\vspace{-4pt}
\resumeSubHeadingListEnd

%--------CORE TECHNICAL SKILLS------------
\section{Core Technical Skills}
 \resumeSubHeadingListStart
    \resumeItemListStart
        \item \textbf{AI \& Deep Learning:} Computer Vision, LLMs, Generative AI, Agentic AI, PyTorch, TensorFlow.
        \item \textbf{Edge AI \& Robotics:} ROS 2, Embedded Deployment (NVIDIA Jetson, Edge Devices), Autonomous Systems (UAV/UGV).
        \item \textbf{Software Engineering:} Python, C++, Docker, Git, CI/CD, Linux, APIs, HPC.
        \item \textbf{Hardware \& Prototyping:} Product Development, 3D Design (CAD) & 3D Printing, System Design
        % \item \textbf{Banking Operations:} Proficient knowledge of internal Consors Finanz (CF) technology, Financial Performance Analysis, Audit-ready Documentation.
    \resumeItemListEnd
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Max Planck Institute for Human Development}}{Berlin, Germany}
      {Research Assistant}{08/2022 -- 03/2026}
      \resumeItemListStart 
        \item Architected end-to-end pipelines and engineered software and AI workflows across 14+ projects.
        \item Employed and fine-tuned LLMs (GPT, Claude, DeepSeek, Gemini) for research tasks.
        \item Automated complex data gathering, model training and technical orchestration for cross-functional research teams.
      \resumeItemListEnd


    \resumeSubheading
      {\textbf{SynergyLabs Technology}}{Gurugram, India}
      {Deep Learning Intern}{11/2021 -- 03/2022}
      \resumeItemListStart
        \item Trained lightweight models that can be run on edge devices like Raspberry Pi and Jetson Nano.
        \item Worked with Nvidia Deepstream and deployed Deep Learning models on Jetson Xavier NX on Indian National Highways.
        \item Orchestrated projects such as Automatic Traffic Counter and Classification, Video Incident Detection Systems, Automatic Number Plate Detection System.
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{iNeuron.ai}}{Bengaluru, India}
      {Data Science Intern}{06/2021 -- 08/2021}
      \resumeItemListStart
        \item Worked on Home Security Automation Project.
        \item With Computer Vision, we tracked motion, face and weapon from CCTV footage to enhance residential security.
      \resumeItemListEnd

    % \resumeSubheading
    %   {\textbf{Sabertooth Technologies}}{Nagpur, India}
    %   {Data Analyst Intern}{10/2020 -- 03/2021}
    %   \resumeItemListStart
    %     \item Engineered custom web spiders to extract, clean, and deliver dataset pipelines from European rental platforms for an international client
    %     \item Contributed to an e-commerce marketplace platform enabling users to aggregate and compare products across multiple websites.
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Science in Artificial Intelligence (M.Sc.)}{05/2022 -- 03/2026}
      {\textbf{Friedrich-Alexander-Universität Erlangen-Nürnberg, Germany}}{GPA: 1.7}
      \resumeItemListStart
        \item \textbf{Focus Areas:} Deep Learning, Computer Vision, Tracking Algorithms
      \resumeItemListEnd

    \resumeSubheading
      {Bachelor of Technology in Information Technology (B.Tech.)}{07/2017 -- 06/2021}
      {\textbf{Guru Gobind Singh Indraprastha University, India}}{Final Grade: 8.32/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects \& Achievements}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Agentic-CV-Maker: AI Application Pipeline}{03/2026}
      {Agentic AI, LLMs, Web Application, Prompt Engineering}{}
      \resumeItemListStart
        \item Vibe-coded an interactive web application leveraging Agentic AI to autonomously parse base resumes, cover letters, and target job descriptions.
        \item Designed an intelligent pipeline that dynamically generates highly tailored, ATS-optimized LaTeX applications and customized interview preparation guides.
      \resumeItemListEnd

  \resumeSubheading
      {Autonomous AI Tracking Robot}{03/2026}
      {ROS 2, Computer Vision (YOLOv8), Edge Hardware, Agentic AI}{}
      \resumeItemListStart
        \item Engineered a fully autonomous, voice-controlled tracking robot integrating a Raspberry Pi, Arduino, and ROS 2 for real-time distributed node communication.
        \item Deployed YOLOv8 and an AI Agent to enable dynamic target lock and physical pursuit via a custom vision-to-motor control loop.
      \resumeItemListEnd

% \resumeSubheading
%       {Robotic Arm \& eVTOL Prototypes}{2026 -- Present}
%       {ROS 2, Agentic AI, Edge Hardware}{}
%       \resumeItemListStart
%         \item Prototyped a custom eVTOL drone and robotic arm, bridging perception and hardware by deploying optimized embedded models onto custom UxV platforms.
%       \resumeItemListEnd

  \resumeSubheading
      {RFID - QR Authentication System}{11/2025}
      {Siemens Healthineers}{}
      \resumeItemListStart
        \item Built a functional offline 2FA prototype in 48 hours, using RFID hardware with a mobile app for highly secure medical devices such as MRI/CT.
        \item Integrated existing Siemens RFID cards with QR codes deployed on an Arduino Nano.
      \resumeItemListEnd

  \resumeSubheading
      {Neuro-SAM -- Foundation Model for 3D Segmentation}{03/2025 -- 09/2025}
      {Anki Lab, AIBE, FAU}{}
      \resumeItemListStart
        \item Explored, Fine-tuned and benchmarked SOTA vision foundation models for segmentation of neural Dendrites and Dendritic Spines.
        \item Developed Neuro-SAM, a novel Python package for tracking and segmenting microscopy data.
      \resumeItemListEnd

  \resumeSubheading
      {2x Hackathon Winner -- Hackoverflow}{01/2024 \& 01/2025}
      {IBA AG \& BEST Erlangen}{}
      \resumeItemListStart
        \item Back-to-back 1st place winner, excelling in rapid prototyping and deployment under strict deadlines.
        \item Engineered an anomaly detection pipeline for time-series sensor data and a full stack web solution. 
      \resumeItemListEnd

    \resumeSubheading
      {Multi-Modal Quality Monitoring System}{05/2024 -- 08/2024}
      {Factory Automation and Processing Systems (FAPS), FAU}{}
      \resumeItemListStart
        \item Developed a Multi-View and Multi-Modal deep learning model leveraging sensor fusion to combine visual (image) and time-series data.
        \item Designed the architecture to perform quality control classification, effectively rejecting faulty electric motors.
      \resumeItemListEnd
      
    \resumeSubheading
      {Hexbug Tracking Olympiad -- 1st Place Winner}{05/2023 -- 07/2023}
      {Department of AI in Biomedical Engineering, FAU}{}
      \resumeItemListStart
        \item Won 1st place by engineering a highly accurate Computer Vision pipeline for tracking the head of erratic moving hexbugs.
        \item Deployed a multi-stage process involving detection, segmentation and tracking.
      \resumeItemListEnd
  

  \resumeSubHeadingListEnd

\section{Publications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dynamics of Content Amplification on TikTok}{02/2026}
      {EPJ Data Science, Springer Nature}{}

  \resumeSubHeadingListEnd


%-----------ADDITIONAL INFORMATION-----------------
\section{Additional Information}
 \resumeSubHeadingListStart
    \resumeSubItem{\textbf{Languages}}{Hindi (Native), English (C1 – Highly Proficient), German (A1)}
    \resumeSubItem{\textbf{Volunteering}}{Served as a volunteer for Akhil Jyot an Initiative by Babu Banarasi Das University, India.}
    \resumeSubItem{\textbf{Interest \& Hobbies}}
        {Team Sports, Cooking, 3D Printing, 3D Design, DIY, Gaming and learning Piano}
 \resumeSubHeadingListEnd


\end{document}