\documentclass[11pt, a4paper]{letter}

% --- PREAMBLE ---
\usepackage{fontspec}
\usepackage[english]{babel}
\usepackage{marvosym}
\usepackage{ragged2e} 
\usepackage[left=2.5cm, right=2.5cm, top=2cm, bottom=2cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\setmainfont{Times New Roman} 

\makeatletter
\renewcommand{\@date}{\today}
\makeatother

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

\begin{document}

\begin{flushleft}
    \textbf{Nipun Arora}  \\
    Erlangen, Germany  \\
    Contact: (+49) 17687826567 | \href{mailto:nipunarora8@yahoo.com}{nipunarora8@yahoo.com} 
\end{flushleft}

\vspace{0.1cm}

\noindent Erlangen, \today

\vspace{0.2 cm}

\begin{flushleft}
    Hiring Manager \\
    Helsing \\
    Berlin / London / Munich
\end{flushleft}

\vspace{0.2 cm}

\noindent \textbf{Subject: Application for AI Research Engineer - Foundational Models}

\vspace{0.2cm}

\noindent Dear Hiring Manager,

\vspace{0.2cm}
I am writing to express my strong interest in the AI Research Engineer position focusing on Foundational Models at Helsing. As an Artificial Intelligence Master's student  graduating in March 2026, I am deeply aligned with Helsing’s mission to protect democracies through technological leadership and ethical AI deployment. Your focus on redefining perception by building foundational intelligence for the physical world perfectly matches my academic focus and hands-on engineering background.
\justifying

\vspace{0.2cm}
What I bring to the foundational intelligence team:
\begin{itemize}
\item \textbf{Vision Foundation Models:} At the Anki Lab, I explored, fine-tuned and benchmarked SOTA vision foundation models for 3D segmentation. This research culminated in the development of Neuro-SAM, a novel Python package for tracking and segmenting complex microscopy data.
\item \textbf{LLM Fine-Tuning \& Large-Scale Data:} As a Research Assistant at the Max Planck Institute , I employed and fine-tuned LLMs (GPT, Claude, DeepSeek, Gemini) for complex research tasks. I have extensive experience in automating complex data gathering, model training and technical orchestration  across 14+ projects.
\item \textbf{First-Principles Engineering \& Research:} I am fluent in Python, and deeply familiar with PyTorch and TensorFlow. I thrive in rigorous research environments and actively contribute to the scientific community, having recently published "Dynamics of Content Amplification on TikTok" in EPJ Data Science, Springer Nature.
\end{itemize}
\justifying

\vspace{0.2cm}
My USP is the combination of advanced AI research from the Max Planck Institute  and a pragmatic software engineering mindset. I do not just import libraries; I build end-to-end pipelines  and bridge the gap between perception algorithms and real-world deployment. 

\vspace{0.2cm}
I am excited about the opportunity to tackle unique AI challenges and contribute to impactful, mission-driven projects alongside world-leading experts at Helsing. I look forward to discussing how my background in multimodal foundation models aligns with your goals.

Thank you for your time and consideration.

\vspace{0.2cm}

\noindent Kind Regards,

\vspace{0.1cm} 

\noindent Nipun Arora 

\end{document}